%-------------------------
% Resume in Latex
% Author : Ali Nemati
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Ali Nemati} & Email : \href{mailto:aliemati1983@gmail.com}{\color{blue}{Aliemati1983@gmail.com}}\\
 % \href{https://www.linkedin.com/in/ali-nemati/}{https://www.linkedin.com/in/ali-nemati/} & Mobile : +1 (971) 400 2132 \\
  
  \href{https://anemati45.wixsite.com/alinemati}{\color{blue}{Anemati45.wixsite.com/alinemati}} &     \href{https://scholar.google.com/citations?hl=en&user=isqivzYAAAAJ&view_op=list_works&sortby=pubdate}{\color{blue}{Ali Nemati Google Scholar}} \\
   \textbf{US Citizenship} & Mobile : +1 (971) 400 2132 \\
  \textbf{Skype ID: }{Ali.nemati63} & \href{https://www.linkedin.com/in/ali-nemati/}{\color{blue}{Linkedin}}
  \\
  \textbf{}{} {Date of Document: \today}
\end{tabular*}

%-----------EDUCATION-----------------
\section{  \textbf{ EDUCATION}  }
  \resumeSubHeadingListStart
     \resumeSubheading
               {University of Wisconsin Milwaukee}{}
      {PhD. Biomedical Health Informatics}{Jan. 2022 -- Jun. 2026}
      
      {Thesis: Using BERT to understand clinical trial eligibility criteria (free-text criteria) and generate judgment of
patients’ eligibility for trials}
      
      
     \resumeSubheading
      {University of Washington}{}
      {Master of Science in Computer Science and Systems }{Sep. 2017 -- Jun. 2019}
      
      {Thesis: Brain Tumor Image Segmentation via Transfer Learning.}
 
   

  \resumeSubHeadingListEnd
%----------------research interest areas------------------
\section{\textbf{FOCUS AREA}}
\begin{itemize}
\item Knowledge of advanced statistical techniques and concepts (regression, properties of distributions, statistical tests and proper usage, etc.) and experience with applications.
 \item Knowledge of a variety of machine learning techniques (clustering, decision tree learning, artificial neural networks, etc.) and their real-world advantages/drawbacks.

\item Running language models to do tasks question answering, fill-mask, text classification and summarization
\item Implementing machine learning techniques and optimization methods (e.g., scalable clustering and data summarization)
\item Applying Statistical metrics of machine learning model (e.g., proving  guarantees on  performance)
\item  Generative modeling and neural networks (e.g., Feature selection and feature extraction) 
\item Visualize partitioning and approximation algorithms to represent the big data (e.g., spectral clustering and related methods)
\item Randomized and reduced numerical linear algebra (e.g., randomized SVD and PCA)
\item Exploring imbalanced and extract pattern of data (e.g., improving robustness and performance of existing methods) 

\end{itemize}

%-----------EXPERIENCE-----------------
\section{ \textbf{ EXPERIENCE }}

  \resumeSubHeadingListStart
  % -----------------Job 0
      \resumeSubheading 
      {Medical College of Wisconsin }{ Wauwatosa , WI, USA}
      {Data Engineer }{Nov. 2020 - May 2022}
      \textbf{Independently designs, implements, develops, maintains complex, and integrates data sources consistent with business requirements and processes on DataShare.}

- The diagnosis of Covid 19 and the need to stay in the hospital utilizing the clinical blood draw may be found at 134 hospitals throughout the state of Wisconsin.

  -  Participating with REDRIRCT team as a data analysis to explore data to the team

   -   Biweekly interpreting, analyzing, and reporting Homicides and Nonfatal Shooting Dashboards\hspace*{0pt}\hfill
    {\color{blue}\href{https://www.mcw.edu/departments/epidemiology/research/milwaukee-homicide-review-commission/reports/dashboards}{ Link}}
    
    - Daily interpreting, analyzing, and reporting Milwaukee County COVID-19 Daily Data

- DataShare REDIRECT Pilot Data Integration
      
      
      
 
  % -----------------Job 1
      \resumeSubheading 
      {Kohls Innovation Center }{ Menomonee Falls, WI, USA}
      {Data Scientist}{Jan. 2020 - July. 2020}
      
      \textbf{- Safety Stock and Top Store Projects:}{  Created Python Scripts to automate pulling data from different Data sources for data-analysis.
      
      \textbf{Implemented Machine Learning} models and application that predicts and recommends levels of safety-stock and top store based on the percentage chance of an order being canceled.}
    %----------- Job 2

    \resumeSubheading
      {University of Washington}{Tacoma, USA}
      {Student Instructor and Lab Assistant}{Sep. 2018 - Jun 2019}
      
       \textbf{- Center for Business Analytics: }{  Responsible for teaching students the various business tools used for Analytics such as \textbf{Tableau, Power BI, and AWS Databricks}.}


    %----------- Job 3
    \resumeSubheading
      {Auckland University of Technology}{ Auckland , New Zealand}
      {Research collaboration}{Jan. 2017 - Dec 2019}
      
       \textbf{- Researching on Glaucoma Disease:}{  The role is cleaning, wrangling data, interpret data and build models using a combination of machine learning algorithms and data. Collaborating with Tennessee University in order to prove our results to publish our paper. }
       

 
  \resumeSubHeadingListEnd
%-----------Real Time project-----------------
\section{\textbf{PROJECTS}}


\resumeSubHeadingListStart




  \item {\textbf{ Chronic Kidney Disease can be affected by high blood pressure :}{ The relationship between High Blood Pressure and Chronic Kidney Disease is investigated by using statistical interpretation and multiple linear regression. Shiny App}}\hspace*{0pt}\hfill
    {\color{blue}\href{https://alinemati.shinyapps.io/CKD-App-main/}{\color{blue} Link}}
    
     \item {\textbf{2022  BC Liquor store prices Shiny App}}
  \hspace*{0pt}\hfill {\href{https://alinemati.shinyapps.io/bcl_new_update/}{ \color{blue} Link}}
  
  
   \item {\textbf{Prediction of Loan Default: }}{Using Tune voter traditional machine learning and Artificial neural network models }
  \hspace*{0pt}\hfill {\href{https://drive.google.com/drive/u/0/folders/13F7ay8FIyjNs6nrtiaTEXjcNOgpWVFGj}{ \color{blue} Link}}

  \resumeSubHeadingListEnd

%-----------Publications-----------------
\section{\textbf{ PUBLICATIONS}}

\begin{enumerate}
    \item[2021]  Norouzifard, M., \textbf{Nemati, A.}, Mollaee, S.,Gholamhosseini H., Black, J., Thompson B, and Turuwhenua J,.  A Comparison of Approaches for Synchronizing Events in Video Streams Using Audio. Submitted THE INTERNATIONAL SYMPOSIUM ON GEOMETRY AND VISION. \hspace*{0pt}\hfill {\color{blue}\href{http://dx.doi.org/10.1007/978-3-030-72073-5_20}{ Link}}
    
    \item[2019] Norouzifard, M., \textbf{Nemati, A.}, Klette, R., GholamHosseini, H., Nouri-Mahdavi, K., \& Yousefi, S. (2019). A hybrid machine learning model to detect glaucoma using retinal nerve fiber layer thickness measurements. Investigative Ophthalmology \& Visual Science, 60(9), 3924-3924. \hspace*{0pt}\hfill {\color{blue}\href{https://iovs.arvojournals.org/article.aspx?articleid=2746956}{ Link}}
    
   \item[2019] Norouzifard, M., \textbf{Nemati, A.}, Klette, R., GholamHosseini, H., Nouri-Mahdavi, K., \& Yousefi, S. (2019). A Fused Pattern Recognition Model to Detect Glaucoma Using Retinal Nerve Fiber Layer Thickness Measurements, Image and Video Technology (pp.1-12)(2019).\hspace*{0pt}\hfill {\color{blue}\href{https://www.springerprofessional.de/en/a-fused-pattern-recognition-model-to-detect-glaucoma-using-retin/17379584}{ Link}}
    
    \item[2019] Norouzifard, M., \textbf{Nemati, A.}, Klette, R., GholamHossieni, H., Nouri-Mahdavi, K., \& Yousefi, S. (2019). Identification of clinically relevant glaucoma biomarkers on fundus images using deep learning. Investigative Ophthalmology \& Visual Science, 60(11), PB090-PB090.\hspace*{0pt}\hfill {\color{blue}\href{https://iovs.arvojournals.org/article.aspx?articleid=2748168}{ Link}}
    
    
    
    \item[2018] Norouzifard M., \textbf{Nemati, A.} , Abdul-Rahman A., GholamHosseini H., Klette R. (2019) A Comparison of Transfer Learning Techniques, Deep Convolutional Neural Network and Multilayer Neural Network Methods for the Diagnosis of Glaucomatous Optic Neuropathy. In: Chang CY., Lin CC., Lin HH. (eds) New Trends in Computer Technologies and Applications. ICS 2018. Communications in Computer and Information Science, vol 1013. Springer, Singapore.\hspace*{0pt}\hfill
    {\color{blue}\href{http://dx.doi.org/10.1007/978-981-13-9190-3_69}{ Link}}
    
    
    \item[2018] Norouzifard, M., \textbf{Nemati, A.}, GholamHosseini, H., Klette, R., Nouri-Mahdavi, K., \& Yousefi, S. (2018, November). Automated glaucoma diagnosis using deep and transfer learning: Proposal of a system for clinical testing. In 2018 International Conference on Image and Vision Computing New Zealand (IVCNZ) (pp. 1-6). IEEE.    \hspace*{0pt}\hfill {\color{blue}\href{http://dx.doi.org/10.1109/IVCNZ.2018.8634671}{ Link}}
    
   \item[2018] \textbf{Nemati, A.}, (2018). Gender and Age Prediction Multilingual Author Profiles Based on Comments. \hspace*{0pt}\hfill {\color{blue}\href{http://ceur-ws.org/Vol-2266/T4-4.pdf}{ Link}}
\end{enumerate}

%----------------Posters ------------------
\section{\textbf{POSTER}}
\begin{enumerate}
    \item[2022]  \textbf{Nemati, A.}, Khani, M.  Using document ranking to classify clinical trial eligibility criteria:\hspace*{0pt}\hfill {\color{blue}\href{https://drive.google.com/file/d/1_Gd3co8i-Me-anvFjnzNBqSyFvdQgESc/view?usp=sharing}{ Link}}
       

\end{enumerate}

%----------------Teaching Assistant) Experience ------------------
\section{\textbf{TEACHING ASSISTANT EXPERIENCE}}
\resumeSubHeadingListStart

       
             \item {TCSS 545B- Database Management (Graduated Teaching Assistant): }\hspace*{0pt}\hfill{Spring 2019}
       
             \item {TCSS 559A- Web Services (Graduated Teaching Assistant):} \hspace*{0pt}\hfill{  Winter 2018}
             
      \resumeSubHeadingListEnd




%--------Award------------
\section{\textbf{ AWARDS}}

\resumeSubHeadingListStart



 \item {\textbf{ 2021 Best paper award in ISGV Auckland}}
  \hspace*{0pt}\hfill {\href{https://doi.org/10.1007/978-981-13-9190-3_69}{ \color{blue} Link}}
  
  \item {\textbf{ 2021 Direct Funds \$ 1500:}{ A Comparison of Approaches for Synchronizing Events in Video Streams Using Audio.}}\hspace*{0pt}\hfill
    {\color{blue}\href{https://link.springer.com/chapter/10.1007\%2F978-3-030-72073-5_20}{\color{blue} Link}}
  %--------------- Award 3
  \item{\textbf{ 2019 Outstanding Paper Awards}{ the International Computer Symposium (ICS), Yunlin, Taiwan}} 
    \hspace*{0pt}\hfill {\color{blue}\href{https://static.wixstatic.com/media/db40d1_26c0561b41b34f4db3d36c0a54c91172~mv2_d_3264_2448_s_4_2.jpg}{ \color{blue}Link}}
    %--------------- Award 2
    \item{\textbf{ 2018 Certificate of the 9th International Cybersecurity Data Mining Competition}}\hspace*{0pt}\hfill
    {\color{red}\href{https://static.wixstatic.com/media/db40d1_0071a864632b46a291aa9e570168510d~mv2.jpg}{ \color{blue}Link}}
      
      
      
      %--------------- Award 1
      \item{\textbf{Volunteer appreciation Award from Impact NW (YMCA)}}\hspace*{0pt}\hfill{\color{blue}\href{https://static.wixstatic.com/media/db40d1_7962f9efd2fc46dc8061aff2dc661a02~mv2.jpeg}{ Link}}

  \resumeSubHeadingListEnd

 



%--------PROGRAMMING SKILLS------------
\section{ \textbf{ PROGRAMMING SKILLS}}
  \resumeSubHeadingListStart
   \item{\textbf{Data Scientist }{: SAS and R programming }}
  \item{\textbf{Machine Learning Techniques}{: Tesnforflow 2.x, PyTorch , Keras, Scikit learn , Ensemble traditional and pre-trained models and Transfer Learning,  LSTM and YOLO3}}
    \item{\textbf{Natural language processing}{: Language model, Bert, N-gram, Sentiment analysis, TFIDF}}
    \item{\textbf{Languages}{: Python 3.x Proficient, Java intermediate , C++ intermediate}}
    \item{ \textbf{Datebase: }}{MySQL, PostgreSQL , Sql Server , BigQuery}
    \item{\textbf{Data Visualization}{: Tableau,  ggplot2, MatplotLib, Seaborn}}
      \item{\textbf{Big Data}{:  PySpark}}
      
      \item{\textbf{Cloud Technologies}{: AWS EC2, S3,  Google Colab, Google Compute, Google Big-Query }}
      \item {\textbf{Others}{: GitHub, jira , Shiny app , The Internet of things}}

  \resumeSubHeadingListEnd






\end{document}
